Crime in Austin Texas: Exploration, Classification, and Trends

### 2024-08-06 products/manuscript/Manuscript.qmd
fixing project repo after submodule issues

```{=html}
<iframe src="/HYLTIN-PII-project/results/figures/html-widgets/new-cat-table.html" width="100%" height="800px" align="centered"></iframe>
```
\
This table is intended to give a general idea of the change of each crime over time and the general quantity relative to others.
We can again see that our specific crime of focus, Murder, is lower than many other types, but is far from the lowest and still has a quantifiable rate.
The sparklines don't do the difference between crimes justice, because there are several that have a far greater rate of occurrence than others, but we can visualize this and the year over year change with the chart below.

@@

```{=html}
<iframe src="/HYLTIN-PII-project/results/figures/static-plots/aggregated-ljung.html" width="100%" height="250px" align="centered"></iframe>
```
\
It is not quite the same story regarding the residuals for murder.
The selected model for the frequency of murder is ARIMA(0,1,1)(0,0,1)~12~.
The plot of the residuals over time is still mostly centered at zero but the variance is less steady than it was for all crime, increasing quite a bit in the last few years, which makes sense since that is when we started to see the rate of Murder increase.
Two spikes in the ACF plot are found to be significant, but this is not terribly abormal since 24 spikes are plotted, and the Ljung-Box test results are also not found to be significant.
The distribution of the residuals is the most questionable, it is fairly asymmetrical so it is unlikely to be normally distributed, but again this is less important than the requirements for uncorrelated and mean 0 residuals.

@@

```{=html}
<iframe src="/HYLTIN-PII-project/results/figures/static-plots/aggregated-ljung.html" width="100%" height="250px" align="centered"></iframe>
```
\
The plots below show these forecasts, the aggregation all crime and for murder, as well as two other crimes picked for their similarity to murder, Aggregated Assault and Unlawful Restraint (kidnapping and similar crimes).
Aggravated Assault was chosen due to its similarity in how the crime is performed, and Unlawful Restraint was chosen due to the number of occurrences being similar to Murder.
The plot for Murder is repeated enlarged for readability.

@@

```{=html}
<iframe src="/HYLTIN-PII-project/results/figures/static-plots/actual-vs-forecast.html" width="100%" height="400px" align="centered"></iframe>
```
## Interpretation and Conlusions

>>>>

```{=html}
<iframe src="../../results/figures/html-widgets/new-cat-table.html" width="100%" height="800px" align="centered"></iframe>
```
\
This table is intended to give a general idea of the change of each crime over time and the general quantity relative to others.
We can again see that our specific crime of focus, Murder, is lower than many other types, but is far from the lowest and still has a quantifiable rate.
The sparklines don't do the difference between crimes justice, because there are several that have a far greater rate of occurrence than others, but we can visualize this and the year over year change with the chart below.

@@

```{=html}
<iframe src="../../results/figures/static-plots/aggregated-ljung.html" width="100%" height="250px" align="centered"></iframe>
```
\
It is not quite the same story regarding the residuals for murder.
The selected model for the frequency of murder is ARIMA(0,1,1)(0,0,1)~12~.
The plot of the residuals over time is still mostly centered at zero but the variance is less steady than it was for all crime, increasing quite a bit in the last few years, which makes sense since that is when we started to see the rate of Murder increase.
Two spikes in the ACF plot are found to be significant, but this is not terribly abormal since 24 spikes are plotted, and the Ljung-Box test results are also not found to be significant.
The distribution of the residuals is the most questionable, it is fairly asymmetrical so it is unlikely to be normally distributed, but again this is less important than the requirements for uncorrelated and mean 0 residuals.

@@

```{=html}
<iframe src="../../results/figures/static-plots/aggregated-ljung.html" width="100%" height="250px" align="centered"></iframe>
```
\
The plots below show these forecasts, the aggregation all crime and for murder, as well as two other crimes picked for their similarity to murder, Aggregated Assault and Unlawful Restraint (kidnapping and similar crimes).
Aggravated Assault was chosen due to its similarity in how the crime is performed, and Unlawful Restraint was chosen due to the number of occurrences being similar to Murder.
The plot for Murder is repeated enlarged for readability.

@@

```{=html}
<iframe src="../../results/figures/static-plots/actual-vs-forecast.html" width="100%" height="400px" align="centered"></iframe>
```
## Interpretation and Conlusions
